The Linguistic Landscape of Stream-of-Consciousness Literature

### 2024-04-03 paper/paper.qmd
update graphs

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce
#| tbl-cap: "Examplary Table of Unprocessed Stream of Consciousness Novels (James Joyce)"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce-token
#| tbl-cap: "Examplary Table of Tokenized Stream of Consciousness Novels (James Joyce)"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce-words
#| tbl-cap: "Examplary Table of Word Count of Stream of Consciousness Novels (James Joyce)"
#| warning: false

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce
#| tbl-cap: "An Examplary Table Containing Unprocessed Novel Text (James Joyce)"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce-token
#| tbl-cap: "An Examplary Table Containing Tokenzied Novel Text (James Joyce)"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce-words
#| tbl-cap: "An Examplary Table Containing Word Count of Each Word within Novel Texts (James Joyce)"
#| warning: false
